---
title: "Alcohol vs Seat choice"
author: "Joel Calderin"
date: "Fall 2023"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

$H_0$ There is no difference in the alcohol consumed based on what row you sit in

$H_A$ There is a difference in the alcohol consumed based on what row you sit in


### Methods

Alcohol is a numerical variable, while seats are categorical variables. This means we use the Numerical~Cat helper file.

### Results

### Graphical Results

```{r}
boxplot(alcohol~Seat,data=davisdata)
```

 
The box plot shows a substantial difference in the alcohol consumed among the 3 rows. The back row consumes the most, while the front and middle row does not consume much at all. 
  

### Numerical Results 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The results for Q3 shows us that there is not a big difference of alcohol consumed in the front and middle row. However, there is a big difference in the amount of alcohol consumed in the back row according to Q3. This helps us conclude that the back row consumes more alcohol than the front and middle row. 

## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The P value is 0.000116 which is less than 0.05. This means we reject the null hypothesis. This means we can conclude that there is a difference in alcohol consumed based on the row that was sat in.

```{r}
plot(TukeyHSD(model1))
```

We have no evidence that there is a difference in the alcohol consumption between the middle and front rows. The only difference we found was that the back row drinks more than the middle and front rows. 

## Conclusions


