---
title: "Alcohol vs Seat choice"
author: "Joel Calderin"
date: "Fall 2023"
output: html_document
---
  
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

$H_0$ There is no difference in the alcohol consumed based on what row you sit in

$H_A$ There is a difference in the alcohol consumed based on what row you sit in


### Methods

Alcohol is a numerical variable, while seats are categorical variables. This means we use the Numerical~Cat helper file.

### Results


### Graphical Results

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

  
  

### Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```


## Inferential Tests

```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

The P value is 0.000116 which is less than 0.05. This means we reject the null hypothesis. This means we can conclude that there is a difference in alcohol consumed based on the row that was sat in.

```{r}
plot(TukeyHSD(model1))
```

We have no evidence that there is a difference in the alcohol consumption between the middle and front rows. The only difference we found was that the back row drinks more than the middle and front rows. 

## Conclusions


